A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-21 tex/main.tex
Readjust to include invasion/resistance.

Using this comparisons of \(x_{N/2}\) are shown in
Figure~\ref{fig:comparison_deterministic}. Note that these are all deterministic
strategies and show a perfect match up between the expected value of
(\ref{equ:fixation_probability}) and the actual Moran process for all
strategies pairs.

@@

Figures~\ref{fig:fixation_heatmap_std} and~\ref{fig:fixation_heatmap_noise}
shows the fixation rates of each player on the y axis against each player on the
x axis.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_std.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_std.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_std.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_std.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_std.pdf}
        \caption{\(N=10\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_std.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_std.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Fixation probabilities of all strategies}
    \label{fig:fixation_heatmap_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_noise.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_noise.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_noise.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_noise.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_noise.pdf}
        \caption{\(N=10\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_noise.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_noise.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Fixation probabilities of all strategies (with noise)}
    \label{fig:fixation_heatmap_std}
\end{figure}

Figure~\ref{fig:histograms_all_fixation_rates_std}
and~\ref{fig:histograms_all_fixation_rates_noise} show the distribution of the
fixation rates for all strategies.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/histograms_all_fixation_rates_std.pdf}
    \caption{Distribution of fixation rates for all players}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/histograms_all_fixation_rates_noise.pdf}
    \caption{Distribution of fixation rates for all players (noise)}
\end{figure}

Figure~\ref{fig:histograms_median_fixation_rates_std}
and~\ref{fig:histograms_median_fixation_rates_noise} show the distribution of the
fixation rates for all strategies.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/histograms_median_fixation_rates_std.pdf}
    \caption{Distribution of median fixation rates for all players}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/histograms_median_fixation_rates_noise.pdf}
    \caption{Distribution of median fixation rates for all players (noise)}
\end{figure}

Figures~\ref{fig:ranks_v_size_standard} and~\ref{fig:ranks_v_size_noisy} show
the median rank of each strategy against population size in the standard and
noisy settings. Note that these ranks are not necessarily integers as group ties
are given the average rank.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_std.pdf}
    \caption{Median rank of players against population size}
    \label{fig:ranks_v_size_standard}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_noisy.pdf}
    \caption{Median  rank of players against population size with noise}
    \label{fig:ranks_v_size_noisy}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_std.pdf}
    \caption{Relationship between Median rank for population size}
    \label{fig:relationship_ranks_v_size_standard}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_noisy.pdf}
    \caption{Relationship between Median rank for population size with noise}
    \label{fig:relationship_ranks_v_size_noise}
\end{figure}

Tables~\ref{tbl:ranks_in_size_2_std},~\ref{tbl:ranks_in_size_14_std},~\ref{tbl:ranks_in_size_2_noisy}
and~\ref{tbl:ranks_in_size_14_noisy} show the rankings across population size
based for the top on bottom performers across the extreme population sizes.

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/top_five_in_size_2_std.tex}
            \label{tbl:top_five_in_size_2_std}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/bottom_five_in_size_2_std.tex}
            \label{tbl:bottom_five_in_size_2_std}
        \end{subfigure}%
        \caption{Performance across population sizes of top and bottom
        performing strategies in population size \(N=2\)}
        \label{tbl:ranks_in_size_2_std}
\end{table}

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/top_five_in_size_14_std.tex}
            \label{tbl:top_five_in_size_14_std}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/bottom_five_in_size_14_std.tex}
            \label{tbl:bottom_five_in_size_14_std}
        \end{subfigure}%
        \caption{Performance across population sizes of top and bottom
        performing strategies in population size \(N=14\)}
        \label{tbl:ranks_in_size_14_std}
\end{table}

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/top_five_in_size_2_noisy.tex}
            \label{tbl:top_five_in_size_2_noisy}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/bottom_five_in_size_2_noisy.tex}
            \label{tbl:bottom_five_in_size_2_noisy}
        \end{subfigure}%
        \caption{Performance across population sizes of top and bottom
        performing strategies in population size \(N=2\) (with noise)}
        \label{tbl:ranks_in_size_2_noisy}
\end{table}

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/top_five_in_size_14_noisy.tex}
            \label{tbl:top_five_in_size_14_noisy}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/bottom_five_in_size_14_noisy.tex}
            \label{tbl:bottom_five_in_size_14_noisy}
        \end{subfigure}%
        \caption{Performance across population sizes of top and bottom
        performing strategies in population size \(N=14\) (with noise)}
        \label{tbl:ranks_in_size_14_noisy}
\end{table}

Table~\ref{tbl:median_rank_v_memory_length} shows the performance based on
memory length.

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/median_rank_v_memory_length_std.tex}
            \caption{Standard}
            \label{tbl:top_five_in_size_14_noisy}
        \end{subfigure}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/median_rank_v_memory_length_noisy.tex}
            \caption{Noisy}
            \label{tbl:bottom_five_in_size_14_noisy}
        \end{subfigure}%
        \caption{Median rank by memory length}
        \label{tbl:median_rank_v_memory_length}
\end{table}

>>>>

Using this comparisons of \(x_{N/2}\) are shown in
Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
values and the line shows the theoretic value. Note that these are all
deterministic strategies and show a perfect match up between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategies pairs.

@@

Figures~\ref{fig:fixation_heatmap_1_std},~\ref{fig:fixation_heatmap_n_over_2_std}
and~\ref{fig:fixation_heatmap_n_over_2_noise} shows the fixation rates of each
player on the y axis against each player on the x axis.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_std.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_1_std.pdf}
        \caption{\((N,i)=(4, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_1_std.pdf}
        \caption{\((N,i)=(6, 1)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_1_std.pdf}
        \caption{\((N,i)=(8, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_1_std.pdf}
        \caption{\((N,i)=(10, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_1_std.pdf}
        \caption{\((N,i)=(12, 1)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_1_std.pdf}
        \caption{\((N,i)=(14, 1)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probability \(x_{1}\) of all strategies}
    \label{fig:fixation_heatmap_1_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_std.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_2_std.pdf}
        \caption{\((N,i)=(4, 2)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_3_std.pdf}
        \caption{\((N,i)=(6, 3)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_4_std.pdf}
        \caption{\((N,i)=(8, 4)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_5_std.pdf}
        \caption{\((N,i)=(10, 5)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_6_std.pdf}
        \caption{\((N,i)=(12, 6)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_7_std.pdf}
        \caption{\((N,i)=(14, 7)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probability \(x_{N/2}\) of all strategies}
    \label{fig:fixation_heatmap_n_over_2_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_noise.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_2_noise.pdf}
        \caption{\((N,i)=(4, 2)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_3_noise.pdf}
        \caption{\((N,i)=(6, 3)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_4_noise.pdf}
        \caption{\((N,i)=(8, 4)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_5_noise.pdf}
        \caption{\((N,i)=(10, 5)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_6_noise.pdf}
        \caption{\((N,i)=(12, 6)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_7_noise.pdf}
        \caption{\((N,i)=(14, 7)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probabilities of all strategies with noise}
    \label{fig:fixation_heatmap_n_over_2_noise}
\end{figure}

Figure~\ref{fig:invasion_boxplot_std} shows the fixation probabilities for each
strategy when invading another strategy.
Figure~\ref{fig:resistance_boxplot_std} shows the fixation probabilities for
each strategy when resisting another strategy.
Figure~\ref{fig:coexistance_boxplot_std} shows the fixation probabilities for
each strategy when initially coexisting with another strategy.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/invasion_boxplot_2_std.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/invasion_boxplot_4_std.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/invasion_boxplot_6_std.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    % TODO be more selective here: just picking out the ones for which we
    % currently have data
    %\begin{subfigure}[htbp]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_8_std.pdf}
        %\caption{\(N=8\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_10_std.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_12_std.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_14_std.pdf}
        %\caption{\(N=14\)}
    %\end{subfigure}%
    \caption{Invasion fixation probabilities of all strategies}
    \label{fig:invasion_boxplot_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/resistance_boxplot_2_std.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/resistance_boxplot_4_std.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/resistance_boxplot_6_std.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    % TODO be more selective here: just picking out the ones for which we
    % currently have data
    %\begin{subfigure}[htbp]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_8_std.pdf}
        %\caption{\(N=8\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_10_std.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_12_std.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_14_std.pdf}
        %\caption{\(N=14\)}
    %\end{subfigure}%
    \caption{Resistance fixation probabilities of all strategies}
    \label{fig:resistance_boxplot_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_2_std.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_4_std.pdf}
        %\caption{\(N=4\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_6_std.pdf}
        %\caption{\(N=6\)}
    %\end{subfigure}%

    \begin{subfigure}[htbp]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_8_std.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_10_std.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_12_std.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_14_std.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Coexistance fixation probabilities of all strategies}
    \label{fig:coexistance_boxplot_std}
\end{figure}

Figures~\ref{fig:ranks_v_size_invasion},~\ref{fig:ranks_v_size_resistance}
and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
population size in the standard and noisy settings. Note that these ranks are
not necessarily integers as group ties are given the average rank.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_invasion.pdf}
    \caption{Invasion}
    \label{fig:ranks_v_size_invasion}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_resistance.pdf}
    \caption{Resistance}
    \label{fig:ranks_v_size_resistance}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_coexist.pdf}
    \caption{Coexistance}
    \label{fig:ranks_v_size_coexist}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_invasion.pdf}
    \caption{Relationship between Median rank for population size for strategies
    invading}
    \label{fig:relationship_ranks_v_size_invasion}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_resistance.pdf}
    \caption{Relationship between Median rank for population size for strategies
    resisting}
    \label{fig:relationship_ranks_v_size_resistance}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_coexist.pdf}
    \caption{Relationship between Median rank for population size for strategies
    coexisting}
    \label{fig:relationship_ranks_v_size_coexist}
\end{figure}

Tables~\ref{tbl:linear_coeficients_std} and~\ref{tbl:linear_coeficients_noisy}
show the coefficients and \(R^2\) value of the linear model relating the rank in
a particular sized population to the ranks in other populations sizes.
% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
% does show that the coefficient of the N=2 column is always low whereas the
% coefficient of the N=14 column is high even in the N=4 row. So how well you do
% in  a match (N=2) has got very little to do with an evolutionary process.

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_invasion.tex"}
        \caption{Linear model coefficients for ranks for invasion}
        \label{tbl:linear_coeficients_invasion}
    \end{subfigure}%
    ~
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_resistance.tex"}
        \caption{Linear model coefficients for ranks for resistance}
        \label{tbl:linear_coeficients_resistance}
    \end{subfigure}

    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_coexist.tex"}
        \caption{Linear model coefficients for ranks for coexistance}
        \label{tbl:linear_coeficients_coexist}
    \end{subfigure}
    \caption{Linear coefficients}
\end{table}
